---
title: "malte_approach"
author: "Victor Møller"
date: "5 dec 2018"
output: html_document
---

### MALTE APPROACH ###

takes quite a while the way I have done it here. 
Mainly because I don't get sample size of the two groups in the three studies & because I can't do the studies at the same time with the syntax lmer(predicted ~ 0 +). I need to get estimates & standard errors for all studies & all groups (6 estimates & standard errors in total.)

Note that now our studies do not agree on the effect of mean. 
JanCo most et al. has a negative value (schizo have lower mean pitch). 

```{r}
#still need schizo data 
schizo_data <- read.csv("schizo_data.csv")
schizo_data <- schizo_data[,-1]
schizo_data$study <- as.factor(schizo_data$study)
schizo_data$diagnosis <- as.factor(schizo_data$diagnosis)

#three subsets 
library(tidyverse)
study1 <- schizo_data %>%
  filter(study == 1)

study2 <- schizo_data %>%
  filter(study == 2)

study4 <- schizo_data %>%
  filter(study == 4)

#This is the study that is fucked now. 
hmm <- study4 %>% 
  group_by(diagnosis) %>%
  summarise(mean = mean(mean))

#models for mean & sd
mean_1 <- lm(mean ~ 0 + diagnosis, data = study1)
sd_1 <- lm(sd ~ 0 + diagnosis, data = study1)
mean_2 <- lm(mean ~ 0 + diagnosis, data = study2)
sd_2 <- lm(sd ~ 0 + diagnosis, data = study2)
mean_3 <- lm(mean ~ 0 + diagnosis, data = study4)
sd_3 <- lm(sd ~ 0 + diagnosis, data = study4)

#statistics 
summary(mean_1)
m1 <- summary(mean_1)
sd1 <- summary(sd_1)
m2 <- summary(mean_2)
sd2 <- summary(sd_2)
m3 <- summary(mean_3)
sd3 <- summary(sd_3)

#finding sd for the estimates 
#standard error * sqrt(n)
coefficients(sd_3)
coef_m1 <- as.data.frame(m1$coefficients[ , 1:2])
coef_sd1 <- as.data.frame(sd1$coefficients[ , 1:2])
coef_m2 <- as.data.frame(m2$coefficients[ , 1:2])
coef_sd2 <- as.data.frame(sd2$coefficients[ , 1:2])
coef_m3 <- as.data.frame(m3$coefficients[ , 1:2])
coef_sd3 <- as.data.frame(sd3$coefficients[ , 1:2])

#putting them together. 
m_coef <- rbind(coef_m1, coef_m2, coef_m3)
sd_coef <- rbind(coef_sd1, coef_sd2, coef_sd3)

#sample size 
supersamle <- schizo_data %>%
  group_by(study, diagnosis) %>%
  summarize(n = n())

#to bind by 
diagnosis <- as.factor(c(0, 1, 0, 1, 0, 1))
study <- as.factor(c(1, 1, 2, 2, 4, 4))

#binding 
sd_coef <- cbind(diagnosis, study, sd_coef)
m_coef <- cbind(diagnosis, study, m_coef)

library(tidyverse)
m_coef <- m_coef %>%
  rename(mean_est = Estimate, mean_std_error = "Std. Error")

sd_coef <- sd_coef %>%
  rename(sd_est = Estimate, sd_std_error = "Std. Error")

#binding more 
all_coef <- merge(sd_coef, m_coef, by = c("diagnosis", "study"))
all_coef_super <- merge(all_coef, supersamle, by = c("diagnosis", "study"))

#calculating SD
with_sd <- all_coef_super %>%
  mutate(sdsd = sd_std_error * sqrt(n)) %>%
  mutate(sdmean = mean_std_error * sqrt(n))

#three different studies - partialing it up. 
schizophrenics <- with_sd %>%
  filter(diagnosis == 1) %>%
  rename("SAMPLE_SIZE_SZ" = "n", "PITCH_F0SD_SZ_M" = "sd_est", "PITCH_F0_SZ_M" = "mean_est", "PITCH_F0_SZ_SD" = "sdmean", "PITCH_F0SD_SZ_SD" = "sdsd") %>%
  ungroup() %>%
  select(-diagnosis, -sd_std_error, -mean_std_error)

healthyctrls <- with_sd %>% 
  filter(diagnosis == 0) %>%
  rename("SAMPLE_SIZE_HC" = "n", "PITCH_F0SD_HC_M" = "sd_est", "PITCH_F0_HC_M" = "mean_est", "PITCH_F0_HC_SD" = "sdmean", "PITCH_F0SD_HC_SD" = "sdsd") %>%
  ungroup() %>%
  select(-diagnosis, -sd_std_error, -mean_std_error)

everything_is_nice <- inner_join(schizophrenics, healthyctrls, by = "study")

#making the three dataframes that we need. 
library(metafor)
PitchRange=escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0_SZ_M,
m2i=PITCH_F0_HC_M, sd1i=PITCH_F0_SZ_SD, sd2i=PITCH_F0_HC_SD,
data = everything_is_nice)

PitchRangeSD=escalc('SMD', n1i=SAMPLE_SIZE_SZ, n2i=SAMPLE_SIZE_HC, m1i=PITCH_F0SD_SZ_M,
m2i=PITCH_F0SD_HC_M, sd1i=PITCH_F0SD_SZ_SD, sd2i=PITCH_F0SD_HC_SD,
data = everything_is_nice)

PitchRange <- filter(PitchRange, complete.cases(PitchRange$yi))
PitchRangeSD <- filter(PitchRangeSD, complete.cases(PitchRangeSD$yi))

colnames(PitchRangeSD)[12] <- "yiSD"
colnames(PitchRangeSD)[13] <- "viSD"

combined <- dplyr::full_join(PitchRange, PitchRangeSD)
write.csv(combined, "ass3_studies_2ndapproach.csv", row.names = FALSE)

```

Checking for difference: 

```{r}

our_data_old_way <- read.csv("ass3_studies.csv")
our_data_new_way <- read.csv("ass3_studies_2ndapproach.csv")

differences <- rbind(our_data_old_way, our_data_new_way)

```

Loading in our data (the old for now)

```{r}
#need meta
meta <- read.csv("meta.csv")

#STUDY ID, SAMPLE_SIZE_SZ, SAMPLE_SIZE_HC, 
our_data <- read.csv("ass3_studies_2ndapproach.csv")
our_data <- our_data %>%
  mutate(StudyID = c(49,50,51)) %>%
  mutate(Article = c("JanCo et al. (3000)", "JanCo more al. (3000)", "JanCo most al. (3000)"))

#crazy try
rbind.match.columns <- function(input1, input2) {
    n.input1 <- ncol(input1)
    n.input2 <- ncol(input2)
 
    if (n.input2 < n.input1) {
        TF.names <- which(names(input2) %in% names(input1))
        column.names <- names(input2[, TF.names])
    } else {
        TF.names <- which(names(input1) %in% names(input2))
        column.names <- names(input1[, TF.names])
    }
 
    return(rbind(input1[, column.names], input2[, column.names]))
}
 
#joining them. 
a3_full <- rbind.match.columns(our_data, meta)
```

two dataframes with own. 

```{r}
a3_mean <- a3_full %>%
  filter(yi != 'NA') %>%
  select(StudyID, Article, SAMPLE_SIZE_SZ, SAMPLE_SIZE_HC, PITCH_F0_SZ_M, PITCH_F0_HC_M, PITCH_F0_SZ_SD, PITCH_F0_HC_SD, yi, vi)

a3_sd <- a3_full %>%
  filter(yiSD != 'NA') %>%
  select(StudyID, Article, SAMPLE_SIZE_SZ, SAMPLE_SIZE_HC, PITCH_F0SD_SZ_M, PITCH_F0SD_HC_M, PITCH_F0SD_SZ_SD, PITCH_F0SD_HC_SD, yiSD, viSD)

```

running analysis on mean 
--> now significant predictor. 

```{r}

a3_m1_mean <- lmer(yi ~ 1 + (1|StudyID), weights = 1/vi, data=a3_mean,
control=lmerControl(check.nobs.vs.nlev="ignore",
check.nobs.vs.nRE="ignore"))

a3_m2_mean <- rma(yi, vi, data = a3_mean, slab=Article)
forest(a3_m2_mean)
a3_m2_mean

```

running analysis on sd
--> still not significant (fucking outlier)

```{r}
a3_m1_sd <- lmer(yiSD ~ 1 + (1|StudyID), weights = 1/viSD, data=a3_sd,
control=lmerControl(check.nobs.vs.nlev="ignore",
check.nobs.vs.nRE="ignore"))

a3_m2_sd <- rma(yiSD, viSD, data = a3_sd, slab=Article)
forest(a3_m2_sd)
a3_m2_sd

```

running confint again. 

```{r}
library(metafor)
confint(a3_m2_mean, level = .95) #interpret. 
confint(a3_m2_sd, level = .95) #interpret. 

```

Influential studies:
--> Cohen is still a crazy outlier. 

```{r}
#mean
inf <- influence(a3_m2_mean)
print(inf)
plot(inf) #study 2 is fucked. 

#sd
inf1 <- influence(a3_m2_sd)
print(inf1)
plot(inf1) #study 6 is fucked. 
```

Funnel plots

```{r}
funnel(a3_m2_mean, main = "Random-Effects Model", xlab = "Standardized Mean
Difference") #something lacking to the left..?

funnel(a3_m2_sd, main = "Random-Effects Model", xlab = "Standardized Mean
Difference") #crazy outlier - difficult to interpret. 
```


#### a4: WITH US, WITHOUT COHEN #### 

Excluding Cohen from the third analysis. 

```{r}

a4_full <- a3_full %>%
  filter(!StudyID %in% c(15))

```

With our study, without Cohen. 
Dataframe for mean (a4_mean) & for sd (a4_sd)

```{r}
a4_mean <- a4_full %>%
  filter(yi != 'NA') %>%
  select(StudyID, Article, SAMPLE_SIZE_SZ, SAMPLE_SIZE_HC, PITCH_F0_SZ_M, PITCH_F0_HC_M, PITCH_F0_SZ_SD, PITCH_F0_HC_SD, yi, vi)

a4_sd <- a4_full %>%
  filter(yiSD != 'NA') %>%
  select(StudyID, Article, SAMPLE_SIZE_SZ, SAMPLE_SIZE_HC, PITCH_F0SD_SZ_M, PITCH_F0SD_HC_M, PITCH_F0SD_SZ_SD, PITCH_F0SD_HC_SD, yiSD, viSD)

```

Model for Mean:
--> surprise, surprise. Also significant without Cohen. 

```{r}
library(metafor)
a4_m1_mean <- lmer(yi ~ 1 + (1|StudyID), weights = 1/vi, data=a4_mean,
control=lmerControl(check.nobs.vs.nlev="ignore",
check.nobs.vs.nRE="ignore"))

a4_m2_mean <- rma(yi, vi, data = a4_mean, slab=Article)
forest(a4_m2_mean)

```

Model for SD 
--> significant without Cohen (as the 2nd analysis)

```{r}

a4_m1_SD <- lmer(yiSD ~ 1 + (1|StudyID), weights = 1/viSD, data=a4_sd,
control=lmerControl(check.nobs.vs.nlev="ignore",
check.nobs.vs.nRE="ignore"))

a4_m2_SD <- rma(yiSD, viSD, data = a4_sd, slab=Article)
forest(a4_m2_SD)
a4_m2_SD

```

Quality check - Heterogeneity
--> Very high heterogeneity. 
--> A lot that is not due to chance. 

```{r}

confint(a4_m2_mean, level = .95) #high
confint(a4_m2_SD, level = .95) #extreme

```

Influential studies. 

COHEN: 
SD in every utterance not across. 
Figure out why it is very different (is it studying something else).
--> if not: multiverse analysis --> do the analysis without Cohen (does this change anything). 


```{r}

#mean
inf <- influence(a4_m2_mean)
print(inf)
plot(inf) #study 2 is fucked. 

#sd
inf1 <- influence(a4_m2_SD)
print(inf1)
plot(inf1) #study 6 is fucked. 

```

Funnelplots - publication bias (needs quantification?). 
--> mean: perhaps lacking studies left of center w. high SE.
--> sd: looks crazy w. high SE studies to the far left (outliers)

```{r}

funnel(a4_m2_mean, main = "Random-Effects Model", xlab = "Standardized Mean
Difference") #still something lacking left with big SE.  

funnel(a4_m2_SD, main = "Random-Effects Model", xlab = "Standardized Mean
Difference") #looks terrible. 

```
